Solution of thermodynamic equilibrium in black-oil reservoirs: the classical material balance equations

### 2014-04-02 pituba/article/article.tex
slow progress.

As previously mentioned, black-oil is a designation to a simplified treatment of hydrocarbon composition and phase equilibrium. Hydrocarbon species are grouped into two pseudo-components called oil and gas, being a pseudo-component one that consists of more than one chemical molecule.

@@

Temperature is thus a constant prescribed value and no energy balance equation is needed. Also, it follows from Gibbs' phase rule that the equilibrium of oil and gas phases has only two degrees of freedom. As temperature is assumed constant, oil phase density in saturated states is a function of pressure or composition only. The same is valid for mass concentrations of gas and oil components in oil phase.

@@

\item gas component:
\begin{equation}\label{eq: Sg2}
\frac{\partial}{\partial t} \int\limits_{\Omega} \left( \rho_o Y_g S_o + \rho_g S_g\right) \phi dV = \rho_g^{ST}Q_g^{ST} \, .
\end{equation}
\end{itemize}
%

@@

The above averaged fluid densities, $\bar{\rho}_w$, $\bar{\rho}_o$ and $\bar{\rho}_g$, may be approximated to a constant value measured at a reference depth, if effects of temperature and compositional gradients are neglected. If we put together the expressions for fluid compressibility and hydrostatic equilibrium, we conclude that density variation with depth is negligible.

>>>>

As already mentioned, black-oil is a designation to a simplified treatment of hydrocarbon composition and phase equilibrium. Hydrocarbon species are grouped into two pseudo-components called oil and gas, being a pseudo-component one that consists of more than one chemical molecule.

@@

Temperature is thus a constant prescribed value and no energy balance equation is needed. Also, it follows from Gibbs' phase rule that the equilibrium of oil and gas phases has only two degrees of freedom (restricting component number to the two pseudo-components). As temperature is assumed constant, oil phase density in saturated states is a function of pressure or composition only. The same is valid for mass concentrations of gas and oil components in oil phase.

@@

\item gas component:
\begin{equation}\label{eq: Sg2}
\frac{\partial}{\partial t} \int\limits_{\Omega} \left( \rho_o Y_g S_o + \rho_g S_g\right) \phi dV = \rho_g^{ST}Q_g^{ST} \, .
\end{equation}
\end{itemize}
%
\subsubsection{Averaging Quantities}

@@

The above averaged fluid densities, $\bar{\rho}_w$, $\bar{\rho}_o$ and $\bar{\rho}_g$, may be approximated to a constant value measured at a reference depth. If we put together the expressions for fluid compressibility and hydrostatic equilibrium, we conclude that density variation with depth is negligible.
